Classifier Testing

### 2019-04-22 Code/dallin_annotations/02_visualize_twitter_data.Rmd
Applied the use of the here::here() function across files 01-09 in dallin_annotations.

library(tidyverse); library(tidytext); library(tm); library(topicmodels)
load("/Users/maddatascientist/DATA SCIENCE/Marketing RA/Twitter Subset2.Rdata") # file location dependent on user
tweets <- twitter_subset

>>>>

# Libraries
library(tidyverse); library(tidytext); library(tm); library(topicmodels)

# Load Data
load(here::here("Data", "Twitter Subset2.Rdata")) # file location dependent on user
tweets <- twitter_subset

### 2019-04-22 Code/dallin_annotations/04_build_fasttext_supervised_classifier.Rmd
Applied the use of the here::here() function across files 01-09 in dallin_annotations.

```{r}
# file_model <- "Output/models/class_mod_1.dat"
# train_data_path <- "Output/clean_data/train_data_1.txt"
# test_data_path <- "Output/clean_data/test_data_1.txt"
```

@@

# tweet_data <- read_csv("data/Marketing Research Labeled Tweets_ - tweet_sample_5k_FULL.csv") %>%  
#  filter(nchar(tweet_text) > 5)
```

>>>>

```{r}
# file_model <- here::here("Output", "models", "class_mod_1.dat")
# train_data_path <- here::here("Output", "clean_data", "train_data_1.txt")
# test_data_path <- here::here("Output", "clean_data", "test_data_1.txt")
```

@@

# tweet_data <- read_csv(here:here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")) %>%  
#  filter(nchar(tweet_text) > 5)
```

### 2019-04-22 Code/dallin_annotations/07_build_classifier.Rmd
Applied the use of the here::here() function across files 01-09 in dallin_annotations.

# file to read tweets from. Should be a txt file with one tweet per line
# file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"
file_txt <- "../../Temporary/tweet_sample_1hM_noRT.txt"

# new file to write the trained model to
file_model50  <- "../../Temporary/model50-tweet_sample_2M_noRT.dat"

@@

# I believe the file I'm linking to will be similar to the one that Adriel linked imported above (commented out).
train <- read_csv("../../Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv") 
# Update: I tried this and I think it causes problems in the code block under "# create a list column..." (currently line 69)

@@

save(train.pr, file = "models/fullClassifierOne/prcomp4.dat")

save(train, file = "models/fullClassifierOne/train_data.dat")

@@

load("models/fullClassifierOne/train_data.dat")

@@

save(bst, file = "models/fullClassifierOne/xgb.modelPC4.dat")
xgb.save(bst, 'models/fullClassifierOne/xgb.modelPC4-xgb_version.dat')
save(test_data, file = "models/fullClassifierOne/test_data.dat")

>>>>

# file to read tweets from. Should be a txt file with one tweet per line
# file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"
file_txt <- here::here("Temporary", "tweet_sample_1hM_noRT.txt")

# new file to write the trained model to
file_model50  <- here::here("Temporary", "model50-tweet_sample_2M_noRT.dat")

@@

# I believe the file I'm linking to will be similar to the one that Adriel linked imported above (commented out).
train <- read_csv(here::here("Temporary", "Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv"))
# Update: I tried this and I think it causes problems in the code block under "# create a list column..." (currently line 69)

@@

save(train.pr, file = here:here("Output", "prcomp4.dat"))

save(train, file = here:here("Output", "train_data.dat"))

@@

load(here:here("Output", "train_data.dat"))

@@

save(bst, file = here:here("Output", "xgb.modelPC4.dat"))
xgb.save(bst, here:here("Output", "xgb.modelPC4-xgb_version.dat"))
save(test_data, file = here::here("Output", "test_data.dat"))

### 2019-04-22 Code/dallin_annotations/09_classifier_testing.Rmd
Applied the use of the here::here() function across files 01-09 in dallin_annotations.

# Libraries
```{r}
library(fastrtext)
library(Matrix)
library(xgboost)
source("../complaint-prediction/R/predict_func.Rmd") # Formerly "R/predict_func.R" in Adriel's original code
source("tweet_complaint_predictor.Rmd") # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
```

##### Reminder of the WD
```{r}
getwd()
```

# Load Models
```{r}
load("../../Temporary/prcomp4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
# Model50 was built in fasttext_clust_EDA

>>>>

# Libraries
```{r}
library(fastrtext)
library(Matrix)
library(xgboost)
source(here::here("Code", "dallin_annotations", "06_define_prediction_functions.R")) # Formerly "R/predict_func.R" in Adriel's original code
source(here::here("Code", "dallin_annotations", "08_define_tweet_complaint_predictor_function.R")) # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
```

##### Reminder of the WD
```{r}
getwd()

here:here()
```

# Load Models
```{r}
load(here::here("Output", "prcomp4.dat")) # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
fasttextModel <- load_model(here:here("Output", "model50-tweet_sample_2M_noRT.dat.bin"))
# Model50 was built in fasttext_clust_EDA
